### 2011-12-14 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\subsection{Description of the Syntax Tree}
Since we modified only the implementation of the output form, the design of the syntax tree remains consequent to the entire design of the analyses. Each node represents a logical component of a query. Inner nodes stand for XQuery constructs that are composed of other constructs and can be further divided. Examples of such constructs are $FLWOR$, $if-than-else$ and function call. Leaf nodes represent elements of XQuery language that cannot be further devided. Typical representants are literal constants. \todo{zistit, ci konstanty nahodou nie su jedine}

>>>>

\subsection{Definition of the Syntax Tree}
\begin{definition}
Syntax tree of a XQuery query $Q$ is a tuple $T = (V, E, o)$ where $V$ is a set of nodes representing XQuery language constructs (TODO\todo{kompletny zoznam}), $E$ is a set of edges - couples $(a,b):a,b \in V$ and $o:V \rightarrow \mathbb{N}$ is an ordering function and $T$ satisfies the following conditions:
\begin{itemize}
\item $(V,E)$ is a tree.
\item The root node is $ModuleNode$ representing the entire query Q.
\item $(a,b)$ is an element of $E$ if and only if $b$ is a direct component of construct $a$ in $Q$.
\item For every node $a \in V$ the ordering function $o$ is defined as follows \\* $o(a) = \left\{
	\begin{array}{ll}
		1  & \mbox{if }a\mbox{ is the root node} \\
		seq(a) & \mbox{else}
	\end{array}
\right.$ \\* where $seq(a)$ is a sequential number of appearence of construct $a$ in $Q$.
\end{itemize}
\end{definition}

\subsection{Description of the Syntax Tree}
Since we modified only the implementation of the output form, the design of the syntax tree remains consequent to the entire design of the analyses. Each node represents a logical component of a query. Inner nodes stand for XQuery constructs that are composed of other constructs and can be further divided. Examples of such constructs are $FLWOR$, $if-than-else$ and function call. Leaf nodes represent elements of XQuery language that cannot be further divided. Typical representants are literal constants. \todo{zistit, ci konstanty nahodou nie su jedine}
